\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\geometry{a4paper}
\geometry{margin=2.5cm,nohead}
\usepackage{amsfonts}
\usepackage[leqno]{amsmath}
\usepackage{rotating}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{proof}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{makeidx}

\newtheorem{definition}{Definition} %[chapter]
\newtheorem{proposition}{Proposition} %[chapter]
\newtheorem{property}{Property} %[chapter]
\newtheorem{lemma}{Lemma} %[chapter]
\newtheorem{theorem}{Theorem} %[chapter]
\newenvironment{proof}{\par\addvspace{\bigskipamount}%
\noindent\textit{Proof.}\ }{\qed\par\addvspace{\bigskipamount}}

\def\squareforqed{\hbox{\rlap{$\sqcap$}$\sqcup$}}
\def\qed{\ifmmode\squareforqed\else{\unskip\nobreak\hfil
\penalty50\hskip1em\null\nobreak\hfil\squareforqed
\parfillskip=0pt\finalhyphendemerits=0\endgraf}\fi}


\newcommand{\codesize}{\small}
\newcommand{\field}[1]{\mathbb{#1}}
\newcommand{\vertex}[1]{\|\,#1\,\|}
\newcommand{\mt}{{\small$\blacktriangle$}}
\newcommand{\leaf}[1]{{\small$\blacktriangle\;$}#1{\small$\;\blacktriangle$}}

\newcommand{\model}{\mathcal{A}} % use: $\model$
\newcommand{\stepRule}[1]{\scriptstyle{ #1}}
\newcommand{\den}[1]{[\![#1]\!]_\model}  % use: $\den{e}$

\graphicspath{{images/}}

\title{Introducing CafeOBJ specifications in the Full Maude database.
Integrating CafeOBJ with the Constructor-based Inductive Theorem
Prover---Programmer Guide%
%\thanks{Research supported by MEC Spanish projects
%\emph{DESAFIOS} (TIN2006-15660-C02-01) and \emph{STAMP}
%(TIN2008-06622-C03-01), and Comunidad de Madrid program
%\emph{PROMESAS} (SÐ0505/TIC/0407).}
}

\author{Adri\'an Riesco\\[.7cm]
% \normalsize Technical Report SIC-7-09\\[1ex]
  \normalsize\textit{Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
  \normalsize\textit{Universidad Complutense de Madrid}\\[.4cm]
  August 2013\\
  (Revised \today)
  }

\date{}
%\institute{}
%\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%
\maketitle

\thispagestyle{empty}
\newpage
\thispagestyle{empty}
\mbox{}\vfill

\begin{abstract}
CafeOBJ and Maude are sister languages of the OBJ language, and two of the most
advanced formal specification languages for systems verification. Although both
of them have a similar syntax and semantics, different usages and applications
have been developed for them. Hence, a tool combining both languages would be very
useful for exploiting the specific features of each of them.

We present here the details of the implementation to load CafeOBJ specifications
into the Full Maude.
We first show how to define the syntax, the functions for parsing, and the rules
to deal with general commands.
%
Then, we present how to extend a specific tool, the Constructor-based Inductive
Theorem Prover (CITP), to deal with CafeOBJ specifications.
This is achieved by creating an attribute that distinguishes the current language,
combining the syntax of both tools, and defining rules that deal with the commands
when our new language is chosen.

\smallskip

%\noindent\textbf{Keywords:} declarative debugging,
%rewriting logic, Maude, metalevel implementation
\end{abstract}

\vfill

\begin{small}
\tableofcontents
\end{small}

\vfill
\mbox{}
\newpage
%\setcounter{page}{1}

\section{Introducing CafeOBJ modules into the Full Maude
database\label{sec:intro}}
\input{intro}

\section{Integrating CafeOBJ with the Constructor-based Inductive Theorem
Prover\label{sec:citp}}
\input{combining.tex}

\subsection{Modifications required in the CITP\label{subsec:citp:modifs}}
\input{modifs.tex}

{\small
\bibliographystyle{abbrv}
\bibliography{../alberto}
}

\end{document}
