\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\geometry{a4paper}
\geometry{margin=2.5cm,nohead}
\usepackage{amsfonts}
\usepackage[leqno]{amsmath}
\usepackage{rotating}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{proof}
\usepackage{alltt}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{makeidx}

\newtheorem{definition}{Definition} %[chapter]
\newtheorem{proposition}{Proposition} %[chapter]
\newtheorem{property}{Property} %[chapter]
\newtheorem{lemma}{Lemma} %[chapter]
\newtheorem{theorem}{Theorem} %[chapter]
\newenvironment{proof}{\par\addvspace{\bigskipamount}%
\noindent\textit{Proof.}\ }{\qed\par\addvspace{\bigskipamount}}

\def\squareforqed{\hbox{\rlap{$\sqcap$}$\sqcup$}}
\def\qed{\ifmmode\squareforqed\else{\unskip\nobreak\hfil
\penalty50\hskip1em\null\nobreak\hfil\squareforqed
\parfillskip=0pt\finalhyphendemerits=0\endgraf}\fi}


\newcommand{\codesize}{\small}
\newcommand{\field}[1]{\mathbb{#1}}
\newcommand{\vertex}[1]{\|\,#1\,\|}
\newcommand{\mt}{{\small$\blacktriangle$}}
\newcommand{\leaf}[1]{{\small$\blacktriangle\;$}#1{\small$\;\blacktriangle$}}

\newcommand{\model}{\mathcal{A}} % use: $\model$
\newcommand{\stepRule}[1]{\scriptstyle{ #1}}
\newcommand{\den}[1]{[\![#1]\!]_\model}  % use: $\den{e}$

\graphicspath{{images/}}

\title{Introducing CafeOBJ specifications in the Full Maude database.
Integrating CafeOBJ with the Constructor-based Inductive Theorem Prover%
%and the Maude Formal Environment
---User Guide%
%\thanks{Research supported by MEC Spanish projects
%\emph{DESAFIOS} (TIN2006-15660-C02-01) and \emph{STAMP}
%(TIN2008-06622-C03-01), and Comunidad de Madrid program
%\emph{PROMESAS} (SÐ0505/TIC/0407).}
}

\author{Adri\'an Riesco\\[.7cm]
% \normalsize Technical Report SIC-7-09\\[1ex]
  \normalsize\textit{Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
  \normalsize\textit{Universidad Complutense de Madrid}\\[.4cm]
  August 2013\\
  (Revised \today)
  }

\date{}
%\institute{}
%\makeindex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%
\maketitle

\thispagestyle{empty}
\newpage
\thispagestyle{empty}
\mbox{}\vfill

\begin{abstract}
CafeOBJ and Maude are sister languages of the OBJ language, and two of the most
advanced formal specification languages for systems verification. Although both
of them have a similar syntax and semantics, different usages and applications
have been developed for them. Hence, a tool combining both languages would be very
useful for exploiting the specific features of each of them.

We present here how to load CafeOBJ specifications into the Full Maude. This is
achieved by defining the CafeOBJ syntax and the rules for parsing these modules.
Since this is the basis of all the applications built on top of Full Maude, an
extra advantage of this process is that we can easily extend other tools to work
with CafeOBJ specifications. 
%
We also present example of such an integration,
namely the Maude Declarative Debugger and the
Constructor-based Inductive Theorem Prover (CITP).
While the Declarative Debugger works with its usual interface,
we have extended the CITP to work specifically with CafeOBJ specifications, so the
underlying Maude infrastructure remains hidden.
%
%We show here two examples of such an integration,
%namely the Constructor-based Inductive Theorem Prover (CITP)
%and the Maude Formal Environment (MFE). While we have extended the former to
%specifically work with CafeOBJ, the latter just uses the Maude modules obtained from
%CafeOBJ specifications.

\smallskip

%\noindent\textbf{Keywords:} declarative debugging,
%rewriting logic, Maude, metalevel implementation
\end{abstract}

\vfill

\begin{small}
\tableofcontents
\end{small}

\vfill
\mbox{}
\newpage
%\setcounter{page}{1}

\section{Introducing CafeOBJ modules into the Full Maude
database\label{sec:intro}}
\input{intro}

\section{Using the Constructor-based Inductive Theorem Prover
\label{sec:using:citp}}
\input{using_citp}

%\section{Using the Maude Formal Environment
%\label{sec:using:mfe}}
%\input{using_mfe}

%\newpage

%\printindex

{\small
\bibliographystyle{abbrv}
\bibliography{../alberto}
}

\appendix

\section{Translation\label{sec:trans}}
\input{translation}

\section{Transforming CafeOBJ files to meet Full Maude requirements\label{app:java}}
\input{app_java}

\end{document}
